Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-12-01 Docs/IJES/journal.tex
reference problems with IJES text

Starting at the 1990s, intensive research was performed in HW-SW partitioning, and several approaches proposed, as shown in~\cite{Arato2003} and~\cite{Mann2007}. In~\cite{Trindade2015,Trindade2016} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT), implemented in a tool called Efficient SMT-Based Context-Bounded Model Checker (ESBMC), in order to perform HW-SW partitioning in embedded systems. The present work extends those studies since there is a substantial improvement in terms of the SMT-based verification method, which has been extended with a multi-core parallel- and binary-search approaches, as well as, the integration of the Maximum SMT (MaxSMT) solver $\nu$Z into ESBMC, which is a state-of-art optimization tool based on SMT~\cite{Bjorner2015}.

>>>>

Starting at the 1990s, intensive research was performed in HW-SW partitioning, and several approaches proposed, as shown in~\cite{Arato2003} and~\cite{Mann2007}. In~\cite{Trindade2015} and~\cite{Trindade2016} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT), implemented in a tool called Efficient SMT-Based Context-Bounded Model Checker (ESBMC), in order to perform HW-SW partitioning in embedded systems. The present work extends those studies since there is a substantial improvement in terms of the SMT-based verification method, which has been extended with a multi-core parallel- and binary-search approaches, as well as, the integration of the Maximum SMT (MaxSMT) solver $\nu$Z into ESBMC, which is a state-of-art optimization tool based on SMT (~\cite{Bjorner2015}).
